---
title: "S.Figure 4"
output: 
  html_document:
    toc: false
    code_folding: hide
mainfont: Helvetica
---

```{css Visuals, include = F, echo = F, eval = T} 

.main-container {
  max-width: 2000px !important;
  margin-left: auto !important;
  margin-right: auto !important;
}
pre {
  max-height: 2000px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
.nobullet li {
  list-style-type: none;
}
.table {
  max-width: 1600px;
}
.table.center {
  margin-left: auto;
  margin-right: auto;
}

```

```{r setup, include=F}

knitr::opts_chunk$set(
  eval=T,echo=F,include=T,message=F,warning=F,fig.width=12,
  fig.height=10,fig.fullwidth=T,fig.align="center"
)

packages <- c(
  "DT","tidyverse","polycor","colorspace","summarytools",
  "arsenal","psych","data.table","dplyr","knitr"
  )

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
# Load all listed packages
suppressPackageStartupMessages(invisible(lapply(packages, library, character.only = TRUE)))

```

```{r read results table,echo=F,include=F,warnings=F,fig.width=8,fig.height=6,out.width='100%',error=T}

Res <- read.csv("../Results/vPGS_associations.csv") %>% 
  mutate(Age=factor(Age)) %>% 
  mutate(Effect=factor(Effect,levels=c("Main","Age","Sex","Home","Ses"))) %>%
  mutate(VarOrGxE=factor(VarOrGxE,levels=c("Var","GxE")))%>% 
  mutate(Model=factor(Model,levels=c("z2","mz","ss","os")))
  
```

# Associations between variance-based polygenic scores (vPGS) and phenotypic variabilty measured in unrelated indiviuals using squared z-scores, and in twin pairs via sibling-differences. 

\newline

```{r,fig.keep='all',out.height='100%',out.width='100%'}
MainPlot <- 
  ggplot(
    Res %>% filter(!((Model=="os"|Model=="ss")&vPGS!="MvPGS")) %>% filter(Rater=="P"),
    aes(x=Age,y=BETA,colour=Model,shape=Effect,alpha=-log10(P))) +
  geom_hline(yintercept=0,colour="yellow",linetype=2)+
  geom_point(position=position_dodge(0.9),size=6) +
  geom_errorbar(aes(ymin=as.numeric(BETA-(1.96*SE)),ymax=as.numeric(BETA+(1.96*SE))),width=.5,position=position_dodge(0.9))+
  facet_grid(VarOrGxE~Outcome,drop=T,scales ="free_x",space="free_x")+
  theme_bw() +
  theme(
    axis.text=element_text(size=12),axis.title=element_text(size=14),# axis.text.x=element_text(angle=45),
    legend.position="bottom",legend.box ="vertical",legend.justification="left",legend.box.just ="left",
    legend.margin=margin(t=0,unit='mm'),legend.spacing=unit(0,'mm'),legend.box.margin=margin(t=0,unit='mm'),
    #plot.margin=margin(t=1,unit='mm'),
    legend.title=element_text(size=14,face="bold"),legend.text=element_text(size=14),
    strip.text=element_text(size=14,color="white"),strip.background=element_rect(fill="#414487FF")
  )+
  labs(y="Beta (95% CI)",x="Age") +
  scale_colour_viridis_d(begin=.2,end=.8,label=c(bquote(unrel-Z^"2"),"MZ-diff","ssDZ-diff","osDZ-diff"))+
  scale_shape_manual("vPGS effect",values=c(15,3,4,8,9),label=c("Main","xAge","xSex","xHomeEnv","xSES"))+
  guides(colour=guide_legend(order=1),shape=guide_legend(order=2),alpha=guide_legend(order=3))

MainPlot
```
\newline

_**Models**: **Z<sup>2</sup>**, squared z-scores regressed on vPGS using a linear model in a sample of unrelated individuals; **MZ-diff**, twin level phenotypic variability computed as the standard deviation (SD) for the twins phenotypic values, regressed on vPGS (identical for MZ twins; twin pair is the unit of analysis); **DZ-diff**, twin level phenotypic-SD values regressed on vPGS-SD values and the mean-vPGS value (vPGS vary in DZ twins; twin pair is the unit of analysis; estimated in same-sex pairs [ss] and opposite-sex pairs separately). vPGS were computed in TEDS participants, using GWA weights estimated from analyses of MoBa participants. LDpred2-auto was used to re-weight marginal SNP effects estimated from GWA, by integrating information from the SNP LD matrix, as well as the heritability and polygenicity of each trait. **Communication**: CCC, Children’s Communication Checklist (Ages 2 - 4); CDI, MacArthur Communicative Development Inventory (Age 9); **Depression**: SMFQ, Short Mood and Feelings Questionnaire; **Hyperactivity & Inattention:** CPRSRS, Conners Parent Rating Scale; **Weight:** residualised for the linear and quadratic effects of height_

\newline
\newline
\newline

## Table of associations: 
```{r View table, warnings=F,out.height='100%',out.width='100%'}

datatable(
  Res %>% filter(!((Model=="os"|Model=="ss")&vPGS!="MvPGS")) %>% filter(Rater=="P")%>%
    select(Outcome,Scale,Age,vPGS,Model,BETA,SE,Z,P,N) %>% 
    mutate(P=formatC(P,digits=2)),
  filter='bottom',extensions='Buttons',rownames=F,
  options=list(
    dom='lfrtiBp',buttons=c('csv'),
    searching=F,pageLength=10,lengthMenu=list(c(10,-1),c('10','All')),scrollX = T,
    columnDefs=list(list(className='dt-left',targets="_all"))
    ))
```