---
title: "Figure 3"
output: 
  html_document:
    toc: false
    code_folding: hide
mainfont: Helvetica
---

```{css Visuals, include = F, echo = F, eval = T} 

.main-container {
  max-width: 2000px !important;
  margin-left: auto !important;
  margin-right: auto !important;
}
pre {
  max-height: 2000px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
.nobullet li {
  list-style-type: none;
}
.table {
  max-width: 1600px;
}
.table.center {
  margin-left: auto;
  margin-right: auto;
}

```

```{r}
remove(list = ls())
```

```{r setup, include=F}

knitr::opts_chunk$set(
  eval=T,echo=F,include=T,message=F,warning=F,fig.width=12,
  fig.height=6,fig.fullwidth=T,fig.align="center"
)

packages <- c(
  "DT","tidyverse","polycor","colorspace","summarytools",
  "arsenal","psych","data.table","dplyr","knitr","ggrepel",
  "directlabels","stringr"
  )

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
# Load all listed packages
suppressPackageStartupMessages(invisible(lapply(packages, library, character.only = TRUE)))

excl <- c(
  "IcqFull","CbclFull","EasFull","CfqFull","ItseaFull","ScqFull","SdqFull","CccFull",
  "SprakFull","NhpicFull","RsdbdFull","PeqFull","SbFull","SclFull","SppaFull","CbclAdhd"
)
```

```{r Load h2 data} 

Paths <- list.files(path="~/Dropbox/Projects/MoBa_vQTL/Results",pattern="h2FullTable.txt",full.names=T)

# h2Tabs[[4]]
# test <- fread(Paths[[4]])

freadh2 <- function(x){
  Tab   <- fread(x)
  if(grepl("_vh2",basename(x))){
    Tab$Analysis<-"vGWA"}else{Tab$Analysis<-"mGWA"}
  # return(Tab)
  # }
  Tab  <- Tab %>% 
    distinct(Trait,.keep_all = T) %>% 
    mutate(Trait=str_replace_all(Trait,"_hAdj",".hAdj")) %>% 
    mutate(Trait=str_replace_all(Trait,"Ch","")) %>% 
    mutate(Trait=str_replace_all(Trait,"Q0","_Q0")) %>% 
    mutate(Trait=str_replace_all(Trait,"Q1","_Q1")) %>% 
    mutate(Trait=str_replace_all(Trait,"__","_")) %>% 
    separate(Trait,c("Trait","Age"),"_") %>% 
    mutate(Trait=ifelse(grepl(x=Age,"hAdj"),paste0(Trait,"hAdj"),Trait)) %>% 
    mutate(Rater=ifelse(grepl(x=Age,"C"),"Child","Mother")) %>% 
    mutate(Age=str_replace_all(Age,".hAdj","")) %>% 
    mutate(Age=str_replace_all(Age,"Q04","6m")) %>% 
    mutate(Age=str_replace_all(Age,"Q05","18m")) %>% 
    mutate(Age=str_replace_all(Age,"Q06","3y")) %>% 
    mutate(Age=str_replace_all(Age,"Q07","5y")) %>% 
    mutate(Age=str_replace_all(Age,"Q09","8y")) %>% 
    mutate(Age=str_replace_all(Age,"Q11C","14y")) %>% 
    mutate(Age=str_replace_all(Age,"Q11M","14y")) %>% 
    mutate(Age=str_replace_all(Age,"0","")) %>% 
    mutate(Age=str_replace_all(Age,"o","")) %>% 
    mutate(Age = factor(Age,
       levels=c("6m","18m","3y","5y","8y","14y"),
       labels=c("6m","18m","3y","5y","8y","14y")
       )) %>% 
    filter(!Trait %in% excl) %>% filter(Trait!="Weight") %>% 
    mutate(Trait=str_replace_all(Trait,".hAdj","")) %>% 
    na.omit()

  return(Tab)
}

h2Tabs  <- lapply(Paths,freadh2)
h2Tab   <- do.call(args=h2Tabs,what="bind_rows")
h2Tably <- datatable(h2Tab)

```

```{r Load N data} 

Paths <- list.files(path="~/Dropbox/Projects/MoBa_vQTL/Results",pattern="vh2SampleSizes",full.names=T)
Tab   <- fread(Paths[1]) 
freadN <- function(x){
  Tab   <- fread(x) %>% 
    mutate(V1=str_replace_all(V1,"GwaSumStats/ChAnthQrs/Ch","")) %>% 
    mutate(V1=str_replace_all(V1,"o_RegenieVQt.Munged.sumstats.gz","")) %>% 
    mutate(V1=str_replace_all(V1,"GwaSumStats/ChPsyGenQrsAsr/Ch","")) %>% 
    mutate(V1=str_replace_all(V1,"Q0","_Q0")) %>% 
    mutate(V1=str_replace_all(V1,"Q1","_Q1")) %>% 
    mutate(V1=str_replace_all(V1,"__","_")) %>% 
    separate(V1,c("Trait","Age"),"_") %>% 
    mutate(Trait=ifelse(grepl(x=Age,"hAdj"),paste0(Trait,"hAdj"),Trait)) %>% 
    mutate(Rater=ifelse(grepl(x=Age,"C"),"Child","Mother")) %>% 
    mutate(Age=str_replace_all(Age,".hAdj","")) %>% 
    mutate(Age=str_replace_all(Age,"Q04","6m")) %>% 
    mutate(Age=str_replace_all(Age,"Q05","18m")) %>% 
    mutate(Age=str_replace_all(Age,"Q06","3y")) %>% 
    mutate(Age=str_replace_all(Age,"Q07","5y")) %>% 
    mutate(Age=str_replace_all(Age,"Q09","8y")) %>% 
    mutate(Age=str_replace_all(Age,"Q11C","14y")) %>% 
    mutate(Age=str_replace_all(Age,"Q11M","14y")) %>% 
    mutate(Age=str_replace_all(Age,"0","")) %>% 
    mutate(Age=str_replace_all(Age,"o","")) %>% 
    mutate(Age = factor(Age,
      levels=c("6m","18m","3y","5y","7y","8y","14y"),
      labels=c("6m","18m","3y","5y","7y","8y","14y")
      )) %>%
    rename(N=V2)
  return(Tab)
}

NTabs   <- lapply(Paths,freadN)
NTab   <- do.call(args=NTabs,what="bind_rows")
NTably <- datatable(NTab)

```


# Relationship between vGWA (y-axis) and mGWA (x-axis) SNP-based heritability estimated using LDSC from summary statistics following GWA and vGWA of childhood behavioural traits in the MoBa sample

```{r Hertiability comparisons, warnings=F,fig.width=11,fig.height=5, out.width='100%'}

h2Tab2  <- h2Tab %>% left_join(NTab,by=c("Trait","Age","Rater"))

h2TabW <- h2Tab %>% distinct(Trait,Age,Analysis,Rater,.keep_all=T) %>% 
  pivot_wider(id_cols=c(Trait,Age,Rater),
              values_from=c(names(h2Tab %>% select(-Trait,-Age,-Analysis,-Rater))),
              names_from=Analysis) %>% na.omit()
Figure_3 <-
  ggplot(
    h2TabW,
    aes(x=h2_mGWA,y=h2_vGWA)) +
  geom_linerange(aes(ymin=round(h2_vGWA-SE_vGWA,2),ymax=round(h2_vGWA+SE_vGWA,2),color=Trait)) +
  geom_linerange(aes(xmin=round(h2_mGWA-SE_mGWA,2),xmax=round(h2_mGWA+SE_mGWA,2),color=Trait)) +
  # scale_x_continuous(limits=c(-0.1,0.2),breaks=c(seq(-.1,.2,0.1)))+
  # scale_y_continuous(limits=c(-0.1,0.2),breaks=c(seq(-.1,.2,0.1)))+
  geom_hline(yintercept=0,colour="limegreen",linetype="dotted") +
  geom_vline(xintercept=0,colour="limegreen",linetype="dotted") +
  facet_wrap(facets=vars(Age),ncol=3) + 
  theme_minimal() +
  scale_colour_viridis_d(option="plasma") +
  guides(color="none")

plotly::ggplotly(Figure_3, tooltip = c("Trait","h2_mGWA","SE_mGWA","h2_vGWA","SE_vGWA"))

```

_Scatter plots display the point estimates (intersection) and standard errors for h<sup>2</sup><sub>mGWA</sub> (x-axis) h<sup>2</sup><sub>vGWA</sub> (y-axis) from all MoBa analyses. The plot is stratified by Age of MoBa participants. MoBa traits are labelled in the hover over boxes (interactive version) and can be viewed in S.Table 6._






```{r}

# h2_TabFull <- fread("Tables_Phe/xIRT_ModelStats.tsv") %>%
#   mutate(Trait=paste0(Scale,Subscale)) %>% 
#   select(Trait,Age=Wave,everything()) %>% 
#   mutate(Rater=ifelse(grepl(x=Age,"C"),"Child","Mother")) %>% 
#   mutate(Trait=str_replace_all(Trait,"Ch","")) %>% 
#   mutate(Age=str_replace_all(Age,"Q04","6mo")) %>% 
#   mutate(Age=str_replace_all(Age,"Q05","18mo")) %>% 
#   mutate(Age=str_replace_all(Age,"Q06","3yr")) %>% 
#   mutate(Age=str_replace_all(Age,"Q07","5yr")) %>% 
#   mutate(Age=str_replace_all(Age,"Q09","8yr")) %>% 
#   mutate(Age=str_replace_all(Age,"Q11C","14yr(c)")) %>% 
#   mutate(Age=str_replace_all(Age,"Q11M","14yr(m)")) %>% 
#   select(!matches("Scale"),!matches("Subscale"),!matches("_"),-AIC) %>% 
#   inner_join(h2Tab2) %>% inner_join(N) %>% 
#   filter(!Trait %in% excl) %>% 
#   mutate(Age=factor(Age,levels=c("6mo","18mo","3yr","5yr","8yr","14yr(m)","14yr(c)"),
#                         labels=c("6 m/o","18 m/o","3 y/o","5 y/o","8 y/o","14 y/o","14 y/o")
#                          )) %>% 
#   mutate(
#     h2_mGWA=round(h2_mGWA,2),h2_vGWA=round(h2_vGWA,2),
#     SE_mGWA=round(SE_mGWA,2),SE_vGWA=round(SE_vGWA,2),
#     lSE_vGWA=round(h2_vGWA-SE_vGWA,2),uSE_vGWA=round(h2_vGWA+SE_vGWA,2),
#     lSE_mGWA=round(h2_mGWA-SE_mGWA,2), uSE_mGWA=round(h2_mGWA+SE_mGWA,2)
#          )
# 
# fwrite(h2_TabFull,"Tables_GenSem/ChPsy/ChPsyh2_FullTable.txt",col.names=T)
# 
# meanh2V  <- round(mean(h2_TabFull$h2_vGWA),2)
# meanZV   <- round(mean(h2_TabFull$Z_vGWA),2)
# meanh2Vz <- round(mean(h2_TabFull %>% filter(Z_vGWA>3) %>% .$h2_vGWA),2)
# meanh2m  <- round(mean(h2_TabFull$h2_mGWA),2)
# meanZm   <- round(mean(h2_TabFull$Z_mGWA),2)
# meanh2mz <- round(mean(h2_TabFull %>% filter(Z_mGWA>3) %>% .$h2_mGWA),2)

```

