---
title: "Figure 1"
output: 
  html_document:
    toc: false
    code_folding: hide
mainfont: Helvetica
---

```{css Visuals, include = F, echo = F, eval = T} 

.main-container {
  max-width: 2000px !important;
  margin-left: auto !important;
  margin-right: auto !important;
}
pre {
  max-height: 2000px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
.nobullet li {
  list-style-type: none;
}
.table {
  max-width: 1600px;
}
.table.center {
  margin-left: auto;
  margin-right: auto;
}

```

```{r setup, include=F}

knitr::opts_chunk$set(
  eval=T,echo=F,include=T,message=F,warning=F,fig.width=12,
  fig.height=6,fig.fullwidth=T,fig.align="center"
)

packages <- c(
  "DT","tidyverse","polycor","colorspace","summarytools",
  "arsenal","psych","data.table","dplyr","knitr"
  )

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
# Load all listed packages
suppressPackageStartupMessages(invisible(lapply(packages, library, character.only = TRUE)))

```

```{r QQplots,echo=F,include=F,warnings=F,fig.width=8,fig.height=6,out.width='100%',error=T}

excl <- c(
  "IcqFull","CbclFull","EasFull","CfqFull","ItseaFull","ScqFull","SdqFull","CccFull",
  "SprakFull","NhpicFull","RsdbdFull","PeqFull","SbFull","SclFull","SppaFull","CbclAdhd"
)
QqPlots <- list.files(path="~/Dropbox/Projects/MoBa_vQTL/Plots/QQ",pattern="QqPlot",full.names=T)
QqPlots <- QqPlots[!grepl(paste(excl,collapse="|"),QqPlots)]

PpPlots <- list.files(path="~/Dropbox/Projects/MoBa_vQTL/Plots/QQ",pattern="PpPlot",full.names=T)
PpPlots <- PpPlots[!grepl(paste(excl,collapse="|"),PpPlots)]

Names   <- str_remove_all(basename(QqPlots),"_QqPlot.png")
Names   <- str_remove_all(Names,"Ch")
Names   <- str_replace_all(Names,"Q04"," 6m")
Names   <- str_replace_all(Names,"Q05"," 18m")
Names   <- str_replace_all(Names,"Q06"," 3y")
Names   <- str_replace_all(Names,"Q07"," 5y")
Names   <- str_replace_all(Names,"Q09"," 8y")
Names   <- str_replace_all(Names,"Q11C"," 14y_c")
Names   <- str_replace_all(Names,"Q11M"," 14y_m")
Names   <- str_replace_all(Names,"_hAdj","")
Names   <- str_replace_all(Names,"mo","m")
Names   <- str_replace_all(Names,"yo","y")
Names   <- str_replace_all(Names,"0","")
Names   <- str_replace_all(Names,"_"," ")
Names   <- str_replace_all(Names,"([a-z])([A-Z])","\\1 \\2")


QQ <- list()
for(i in seq_along(QqPlots)){
  QQ[[i]] <- cowplot::ggdraw() + cowplot::draw_image(paste0(QqPlots[[i]]))
}

PP <- list()
for(i in seq_along(PpPlots)){
  PP[[i]] <- cowplot::ggdraw() + cowplot::draw_image(paste0(PpPlots[[i]]))
}

QQPP <- list()
for(i in seq_along(PpPlots)){
  QQPP[[i]] <- cowplot::plot_grid(QQ[[i]],PP[[i]],ncol=2,rel_widths=c(.45,.55))
}

rm(PP);rm(QQ)

```


# Genome-wide SNP association p-values, plotted as quantile-quantile (left) and scatter plots (right) for vGWA and mGWA p-values {.tabset .tabset-dropdown}

_Quantile-quantile plots (left) display the expected and observed -log10 p-values from GWA (+) and vGWA (x) and scatter plots (right) show the relationship between p-values for SNPs estimated from vGWA (quantile integrated rank scores) on the y-axis and GWA (factor scores) on the x-axis. Outcomes include psychometrically measured behavioural traits, and height and weight. _

```{r, results='asis',error=T,fig.keep='all',out.height='100%',out.width='100%'}
for(i in seq_along(QQPP)){
  cat("## ", paste0(Names[[i]]), "\n")
  cat("\n");print(QQPP[[i]]);cat("\n");cat("\n")
}
```

_ICQ6, Infant Characteristics Questionnaire 6 Months Form; ASQ, Ages and Stages Questionnaires; EAS, Emotionality, Activity and Shyness Temperament Questionnaire; CBCL, Child Behaviour CheckList; AUTQ, Early Screening of Autistic Traits Questionnaire-Short (+Modified Checklist for Autism in Toddlers); ITSEA, Infant-Toddler Social and Emotional Assessment; CFQ, The Child Feeding Questionnaire; SDQ, Strength and Difficulties Questionnaire-Prosocial Subscale; SCQ, Social Communication Questionnaire; PPBS, Preschool Play Behaviour Scale; CPRSRS, Conners Parent Rating Scale - Revised, Short Form; CCC, Children’s Communication Checklist-2 Short: Coherence I; SPRAK, Statements about Language-Related Difficulties: Semantics; SLAS, Speech and Language Assessment Scale; CAST, Childhood Asperger Syndrome Test; RSDBD, Rating Scale for Disruptive Behaviour Disorders; CEBQ, Children’s Eating Behaviour Questionnaire; SCARED, Screen for Child Anxiety Related Disorders; SMFQ, Short Mood and Feelings Questionnaire; SPIN, Mini Social Phobia Inventory; NHPIC30, Short Norwegian Hierarchical Personality Inventory for Children; PEQ, Parental Environment Questionnaire; YPTI, Youth Psychopathic Traits; CAPE15, Community Assessment of Psychic Experiences; SCL, The (Hopkins) Symptoms Checklist; DES, Differential Emotional Scale; RSES, Rosenberg Self-Esteem Scale; SWLS, Satisfaction with life scale; IPIP, International Personality Item Pool; SFS, School Functioning Scale; SPPA, Self-Perception Profile for Adolescents; SB, School belonging_

# {.tabset .tabset-dropdown}

```{r, results='asis',error=T,fig.keep='all',out.height='100%',out.width='100%',eval=F}
for(i in seq_along(QQPP)){
  cat("## ", paste0(Names[[i]]), "\n")
  cat("\n");print(QQPP[[i]]);cat("\n");cat("\n")
}
```

# 

```{r}
```


