---
title: "Figure 2"
output: 
  html_document:
    toc: false
    code_folding: hide
mainfont: Helvetica
---

```{css Visuals, include = F, echo = F, eval = T} 

.main-container {
  max-width: 2000px !important;
  margin-left: auto !important;
  margin-right: auto !important;
}
pre {
  max-height: 2000px !important;
  overflow-y: auto !important;
  overflow-x: scroll !important;
}
.nobullet li {
  list-style-type: none;
}
.table {
  max-width: 1600px;
}
.table.center {
  margin-left: auto;
  margin-right: auto;
}

```

```{r setup, include=F}

knitr::opts_chunk$set(
  eval=T,echo=F,include=T,message=F,warning=F,fig.width=12,
  fig.height=6,fig.fullwidth=T,fig.align="center"
)

packages <- c(
  "DT","tidyverse","polycor","colorspace","summarytools",
  "arsenal","psych","data.table","dplyr","knitr","ggrepel",
  "directlabels","stringr"
  )

installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
# Load all listed packages
suppressPackageStartupMessages(invisible(lapply(packages, library, character.only = TRUE)))

```

```{r, fig.height=4,fig.width=8,warning=F,eval=T}

PheWasPaths <- list.files(path="~/Dropbox/Projects/MoBa_vQTL/Results",pattern="PheWas",full.names=T)

freadPheWas <- function(x){
  Tab  <- fread(x)
  if(grepl("_v",basename(x))){
    Tab$MoBaAnalysis<-"vQTL"}else{Tab$MoBaAnalysis<-"mQTL"}
  if(grepl("Anth",basename(x))){
    Tab$MoBaTrait<-paste0(Tab$MoBaTrait,Tab$Age)}
  Tab  <- Tab %>% 
    mutate(GwasP=ifelse(MoBaAnalysis=="mQTL",mP,vP)) %>% 
    arrange(PheWasP) %>% distinct(PheWasTrait,MoBaTrait,.keep_all=T) %>% 
    mutate(Label=str_replace_all(PheWasTrait,"\\s*\\([^\\)]+\\)","")) %>% 
    mutate(Label=str_replace_all(Label,"[[:punct:]]","")) %>% 
    mutate(Label=str_to_title(Label)) %>% 
    mutate(Label=str_replace_all(Label," ","")) %>% 
    mutate(Label=str_replace_all(Label, "CellCount", "Count")) %>% 
    distinct(Label,MoBaTrait,.keep_all=T) %>% 
    select(Label,PheWasTrait,MoBaTrait,MoBaAnalysis,GwasP,PheWasP,rsid) %>% distinct() %>% 
    mutate(MoBaTrait=str_replace_all(MoBaTrait, "C_", " ")) %>% 
    mutate(MoBaTrait=str_replace_all(MoBaTrait, "Full", "")) %>% 
    mutate(MoBaTrait=str_replace_all(MoBaTrait, "([a-z])([A-Z])", "\\1 \\2")) %>% 
    mutate(MoBaTrait=str_replace_all(MoBaTrait, "([a-z])([0-9])", "\\1_\\2")) %>% 
    mutate(MoBaTrait=str_replace_all(MoBaTrait, "([a-z]) ([0-9])", "\\1_\\2")) %>% 
    separate(MoBaTrait,c("MoBaTrait","Age"),"_") %>% 
    mutate(Age = factor(Age,
      levels=c("6mo","18mo","03yo","3yr","05yo","5yr","07yo","08yo","8yr","14yo","14yr"),
      labels=c("6m","18m","3y","3y","5y","5y","7y","8y","8y","14y","14y")
      )) %>% 
    mutate(MoBaTrait2=MoBaTrait) %>% 
    separate(MoBaTrait2,c("Scale","Subscale")," ") %>% 
    select(MoBaTrait,Scale,Subscale,everything()) %>% 
    mutate(Scale=factor(Scale,levels=c("Asq","Eas","Icq","Itsea","Rsdbd","Scq","Smfq","Sppa","Sprak","Height","Weight")))     
  return(Tab)
}

PheWasTabs <- lapply(PheWasPaths,freadPheWas)
PheWasTabs <- do.call(args=PheWasTabs,what="bind_rows")
PheWasTab  <- datatable(PheWasTabs)

PheWasPlot <- 
  ggplot(
    PheWasTabs,
    aes(y=-log10(PheWasP),x=Age,shape=MoBaAnalysis,size=-log10(GwasP),colour=Age,
        label1=MoBaTrait,label2=PheWasTrait))+ #colour=-log10(GwasP)))+ 
    geom_point(position=position_jitter(seed=1),show.legend=F)+
    theme_minimal()+
    scale_colour_viridis_d(begin=.2,end=.8)+
    facet_grid(rows=vars(MoBaAnalysis),cols=vars(Scale),drop=T,scales="free_y")+
    scale_shape_manual(values = c("mQTL"=3,"vQTL"=4))+
    geom_text_repel(
      aes(label=Label),box.padding=1,max.overlaps=15,show.legend=F,direction="both",
      size=2,position=position_jitter(seed=1),angle=0)+
    theme(axis.text.x=element_blank(),strip.text=element_text(size=8))

# ggsave(
#   vPheWasPlot,
#   file="Dropbox/Projects/Analyses/vPheWasPlot.png",
#   device="png",width=2400,height=1200,units="px"
#   )

PheWasPlotly <- 
  plotly::ggplotly(PheWasPlot,
    tooltip=c("label1","label2","size","x","y")
      # paste(
      #   "MoBaTrait:",PheWasPlot$data$label1,"<br>",
      #   "Age:",PheWasPlot$data$size,"<br>",
      #   "PheWasTrait:",PheWasPlot$data$label2,"<br>",
      #   "GwasP:",PheWasPlot$data$x,"<br>",
      #   "PheWasP:",PheWasPlot$data$y
      #   )
      ) %>%
  plotly::layout(showlegend = FALSE)

iPheWasPlots<-list()
for(i in seq_along(unique(PheWasTabs$Scale))){
  iPheWasPlots[[i]]<-ggplot(PheWasTabs %>% filter(Scale==unique(PheWasTabs$Scale)[i]),
      aes(y=-log10(PheWasP),x=Age,shape=MoBaAnalysis,size=-log10(GwasP),colour=Age,
          label1=MoBaTrait,label2=PheWasTrait))+
      geom_point(position=position_jitter(seed=1),show.legend=F)+
      theme_minimal()+
      scale_colour_viridis_d(begin=.2,end=.8)+
      facet_grid(rows=vars(MoBaAnalysis),drop=T,scales="free_y")+
      scale_shape_manual(values = c("mQTL"=3,"vQTL"=4))+
      geom_text_repel(
        aes(label=Label),box.padding=1,max.overlaps=15,show.legend=F,direction="both",
        size=2,position=position_jitter(seed=1),angle=0)+
      theme(axis.text.x=element_blank(),strip.text=element_text(size=8))
}

```

# Phenome-wide association study associations, for all effectively independent (r<.1) SNPs with GWA and vGWA association p-values < 1x10-5 for A. mQTL (top panel) and B. vQTL (bottom panel).

_Scatter plots display the -log10 GWA p-values from publicly available datasets (PheWasP; y-axis) and -log10 p-values from MoBa GWA and vGWA analyses (x-axis) of psychometrically measured behavioural outcomes and height and weight. The plot is stratified by Age of MoBa participants, with age increasing from left to right (x-strip; colour) and by the type of analysis (y-strip), with mGWA (+) in the top panel and vGWA (x) in the bottom panel. PheWas traits are labelled in hover over boxes (interactive version only)_

```{r, fig.height=4,fig.width=8,warning=F}
PheWasPlotly
```



# By scale: {.tabset .tabset-dropdown}

```{r, results='asis',error=T,fig.keep='all',out.height='100%',out.width='100%'}
for(i in seq_along(unique(PheWasTabs$Scale))){
  cat("## ", paste0(unique(PheWasTabs$Scale)[i]), "\n")
  cat("\n");print(iPheWasPlots[[i]]);cat("\n");cat("\n")
}
```

# Phenome-wide association study associations

```{r}
PheWasTab
```